Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-01-27 followup.tex
Almost finished the proof of geotypes, assuming conjecture geoWeil.
Moving to a different computer.

%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\OL}{\mathcal{O}_L}
\newcommand{\OO}[1]{\mathcal{O}_{#1}}
\newcommand{\bFq}{\bar{k}}
\newcommand{\Fq}{k}
\newcommand{\Fqm}{k_m}
\newcommand{\EEx}{\EE^\times}
\newcommand{\ZEx}{\mathbb{\bar Z}_\ell^\times}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\m}{{\mathfrak{m}}}
%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\DeclareMathOperator{\GL}{GL}
\newcommand{\comp}{\Pi} % Component group
\newcommand{\G}{\textbf{G}}
%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
\DeclareMathOperator{\Gal}{Gal}
\newcommand{\Frob}[1]{\operatorname{Fr}_{#1}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\obj}{obj}
\DeclareMathOperator{\mor}{mor}
\DeclareMathOperator{\Lang}{Lang}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\Loc}{Loc}
\DeclareMathOperator{\Tot}{Tot}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\PGL}{PGL}
\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
\newcommand{\op}{_{\operatorname{op}}}
\newcommand{\der}{_{\operatorname{der}}}
\newcommand{\ab}{_{\operatorname{ab}}}

@@

In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ and writing $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
\[
\begin{tikzcd}
\Frob{}^* \gcs{L} \arrow{d}[swap]{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
\gcs{L} \arrow{r}{\alpha} & \gcs{L}
\end{tikzcd}
\]
commutes, where $\cs{L}'$ refers to $(\gcs{L}',\phi')$.
While this simplifies notation considerably, it is, unfortunately, not consistent with our earlier paper.

@@

We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
%Then we have the diagram
%\[
%\begin{tikzcd}
%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
%G & & G \\
%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
%\end{tikzcd}
%\]
Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
\[
\beta : \cs{L}\vert_H \to (\EE)_{H}
\]
by 
\begin{equation}\label{betanu}
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\end{equation}
or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
\[
\begin{tikzcd}[column sep=30]
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The next lemma makes that statement more precise.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
%
In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.

@@

\begin{proposition}\label{prop:quasicharacters}
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$. \todo{Missing proof}
\end{proposition}

@@

\subsection{Review of Jacobi theory over finite fields}

For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.

@@

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\[
\begin{tikzcd}
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} &&
\end{tikzcd}
\]
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
By \cite{yu:01a}*{}, the representation 
\[
h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
\] 
of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$. This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}

@@

@@

\subsection{Geometrization of characters of types}\label{ssec:geometrization}

\todo{Everything below here is under construction}

We begin explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
\begin{enumerate}
\item A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
\[
\trFrob{\bar A} = \trace \sigma.
\]
The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then $\trFrob{\bar B} = \trace \tau$ so
\[
\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
\]
where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.

\item For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$. 
\item For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
\end{enumerate}

\begin{proposition}\label{prop:types}
Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
With notation as above, suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Then there is a virtual admissible Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
\end{proposition}

@@

>>>>

      \newtheorem{conjecture}[theorem]{Conjecture}
%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\OL}{\mathcal{O}_L}
\newcommand{\OO}[1]{\mathcal{O}_{#1}}
\newcommand{\bFq}{\bar{k}}
\newcommand{\Fq}{k}
\newcommand{\Fqm}{k_m}
\newcommand{\EEx}{\EE^\times}
\newcommand{\ZEx}{\mathbb{\bar Z}_\ell^\times}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\m}{{\mathfrak{m}}}
%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\DeclareMathOperator{\GL}{GL}
\newcommand{\comp}{\Pi} % Component group
\newcommand{\G}{\textbf{G}}
%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
\DeclareMathOperator{\Gal}{Gal}
\newcommand{\Frob}[1]{\operatorname{Fr}_{#1}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\obj}{obj}
\DeclareMathOperator{\mor}{mor}
\DeclareMathOperator{\Lang}{Lang}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\Loc}{Loc}
\DeclareMathOperator{\Tot}{Tot}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\PGL}{PGL}
\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
\newcommand{\op}{_{\operatorname{op}}}
\newcommand{\der}{_{\operatorname{der}}}
\newcommand{\ab}{_{\operatorname{ab}}}

@@

In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves. 
We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$. 
We will also write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
\[
\begin{tikzcd}
\Frob{}^* \gcs{L} \arrow{d}[swap]{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
\gcs{L} \arrow{r}{\alpha} & \gcs{L}
\end{tikzcd}
\]
commutes, where $\cs{L}'$ refers to $(\gcs{L}',\phi')$.
While this simplifies notation considerably, it is, unfortunately, not consistent with our earlier paper.

@@

We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
%Then we have the diagram
%\[
%\begin{tikzcd}
%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
%G & & G \\
%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
%\end{tikzcd}
%\]
Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
$
\beta : \cs{L}\vert_H \to (\EE)_{H}
$
by 
\begin{equation}\label{betanu}
\nu = (\beta \boxtimes \id) \circ  f^*\mu,
\end{equation}
or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
\[
\begin{tikzcd}[column sep=30]
\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
\end{tikzcd}
\]
In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
The next lemma makes that statement more precise.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
%
In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of the Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.

@@

\begin{proposition}\label{prop:quasicharacters}
Let $\underline{G}$ be a smooth group scheme over $\OK$.
Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
\end{proposition}

@@

\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}

%For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.

@@

\begin{conjecture}\label{conj:Jacobi}
For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as in Section~\ref{sec:Jacobi}, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
\end{conjecture}

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
By \cite{yu:01a}*{}, the representation 
\begin{equation}\label{eq:tensor}
h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$. This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}

@@

Consider the following diagram of smooth group schemes over $\OK$ and compare with \eqref{eq:semiprod}.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}

@@

\subsection{Geometrization of characters of types}\label{ssec:geotypes}

\begin{proposition}\label{prop:geotypes}
Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
Assume Conjecture~\ref{conj:Jacobi}.
and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
Then there is a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
\end{proposition}

\begin{proof}
%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.

By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \CC^\times\\
& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \sigma.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^+$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^+} = \trace \tau.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}. 
With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
Factor
\[
\begin{tikzcd}
\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \CC\\
& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
\end{tikzcd}
\]
Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
\[
\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.

Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
Let $\cs{W}^{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
\[
\trFrob{\cs{W}^{i+1}} = \trace(W_{i+1}).
\]
Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W^{i+1}$ by pullback. 
Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
$\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{\OK}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.

We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
We have already defined $\cs{A}^0_m$.
Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.

Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
&& G_m^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
\[
(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
Consider the sheaf 
\[
\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
\[
\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
\]
%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
Before continuing, let us calculate: 
\begin{eqnarray*}
\trFrob{\cs{\tilde A}^{i+1}_m}(x)
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
\end{eqnarray*}
Now, 
\[
y \mapsto \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
\]
is precisely 
\[
\begin{tikzcd}
\end{tikzcd}
\]

@@

A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then $\trFrob{\bar B} = \trace \tau$ so
\[
\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
\]
where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.

%\item 
For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$.

%\item
For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
%\end{enumerate}
